### 2017-04-02 paper/modes.tex
minor changes section 2

The list below shows the choices to control parallelism within one
Java virtual machine (JVM), which runs in a single CPU process.  These
options are offered by the testing framework, \eg{}, JUnit.

@@

The list below shows the choices to control parallelism through build
systems which uses multiple JVMs on different processes each:

\begin{itemize}
\item
    \textbf{Forked classes; sequential methods (\ForkSeq).}~This
        configuration corresponds to the parallel execution of test
        classes on different JVMs with test methods running
        sequentially within each JVM.
\item
    \textbf{Forked classes; parallel methods (\ForkParMeth).}~This
        configuration corresponds to the parallel execution of test
        classes on different JVMs with test methods running on
        multiple threads within each JVM.
\end{itemize}

>>>>

The list below shows the choices to control parallelism within one
Java Virtual Machine (JVM), which runs in a single CPU process.  These
options are offered by the testing framework, \eg{}, JUnit.

@@

The list below shows the choices to control parallelism through the
build system, \eg{}, Maven.  The build system can spaw multiple JVMs,
each running on its own OS process on a given CPU and handling a
partition of the test set.

\begin{itemize}
\item
    \textbf{Forked classes; sequential methods (\ForkSeq).}~This
    configuration spawns multiple JVMs, assigning a partition of the
    test set to each JVM.  Test methods run sequentially within each
    JVM.
\item
    \textbf{Forked classes; parallel methods (\ForkParMeth).}~In
    addition to forking multiple JVMs, as \ForkSeq{} does, this
    configuration runs tests concurrently, as \SeqClassParMeth{} does.
\end{itemize}
